### 2015-07-05 narrative/naming-service.tex

>>>>

Our research in this area will address the following questions:\\
   Which data block and what quality/type do we respond to a query
    with?;\\
   How will we scale a fully distributed storage system's metadata
    management;\\
   Can we accelerate the discovery process with the addition of an
    application/user level metadata store that tracks where data was
    originally written and how was it structured?;\\
   Can we provide time estimates for read/write calls in the presence of
    an unbounded discovery system? If not how do we bound the discovery time?
   How do we amortize the time cost of discovery vs time cost of actually reading the data
    (latency vs bandwidth essentially)?

### 2015-07-05 narrative/qos.tex

In this proposal we will investigate the trade-off in terms of predictable peformance between ``filing'' data, making an upfront investment to ensure finding data quickly, and ``piling'' data, pushing the cost of finding to the moment when the data is actually needed. This trade-off has a parallel in data management where there are two alternative paths to achieve knowledge: the analogue to filing is ``extract, transform, and load'' (ETL) data into a warehouse, paying an upfront ingest cost to achieve fast querying; the analogue to piling is to not pay any upfront cost and query the raw data directly by using data processing platforms such as Hadoop. Recent work has found that the combination of these two techniques can be optimized to perform better than any one technique alone~\cite{lefevre:sigmod14a}. We believe that a similar opportunity exists for combining filing and piling approaches to achieve performance predictability without sacrificing too much flexibility.

@@

>>>>

In this proposal we will investigate the trade-off in terms of predictable performance between ``filing'' data, making an upfront investment to ensure finding data quickly, and ``piling'' data, pushing the cost of finding to the moment when the data is actually needed. This trade-off has a parallel in data management where there are two alternative paths to achieve knowledge: the analogue to filing is ``extract, transform, and load'' (ETL) data into a warehouse, paying an upfront ingest cost to achieve fast querying; the analogue to piling is to not pay any upfront cost and query the raw data directly by using data processing platforms such as Hadoop. Recent work has found that the combination of these two techniques can be optimized to perform better than any one technique alone~\cite{lefevre:sigmod14a}. We believe that a similar opportunity exists for combining filing and piling approaches to achieve performance predictability without sacrificing too much flexibility.

@@

Specifically, we will address the following research questions:\\
  1) Can we make any guarantees in a scalable decentralized system?; \\
  2) What quality of service metrics can be make guarantees on in a scalable
    way?;\\
  3) What kind of error rates will we have in our estimation and what error
    rates are acceptable?;\\
  4) How much will the qos scheduler, admission control, manager cost in
    terms of resources and time?;\\
  5) How do we make the scheduler scalable with the size of the system?
